### 2021-03-31 papers.tex
add badges for all artifact papers, less one

\newcommand{\link}[2][]{\vspace{-1in} {\scriptsize #1 \url{#2}} \raisebox{-0.5\height}{\includegraphics[height=0.75in]{participation}}}

\addtrack
    {}{Fun(?) and Games Track}
\addpaper
    {Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
    {Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}
    {Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}
    {SIGBOVIK_2021_paper_5}
    {0cm}
    {}
\addpaper
    {Demystifying the Mortal Kombat Song}
    {J Devi and Chai-Tea Latte}
    {Keywords: mortal-kombat, truth, meaning-of-life}
    {SIGBOVIK_2021_paper_12}
    {0cm}
    {}
\addpaper
    {Unicode Magic Tricks}
    {Nicolas Hurtubise}
    {Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}
    {SIGBOVIK_2021_paper_13}
    {0cm}
    {}
\addpaper
    {Video games in Fonts Fontemon}
    {Michael Mulet}
    {Keywords: font, video game, font video game, silly idea done seriously}
    {SIGBOVIK_2021_paper_18}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_5}
    {0cm}

\addpaper
    {Soliterrible}
    {Sam Stern}
    {Keywords: solitaire, klondike, cards}
    {SIGBOVIK_2021_paper_27}
    {0cm}
    {}
\addpaper
    {Opening Moves in 1830: Strategy in Resolving the N-way Prisoner’s Dilemma}
    {Philihp Busby and Daniel Ribeiro E Sousa}
    {Keywords: boardgame, opening, strategy, deterministic, auction}
    {SIGBOVIK_2021_paper_44}
    {0cm}
    {}

@@

\addtrack
    {}{``Type'' Track}
\addpaper
    {Stop Doing Type Theory}
    {}
    {Keywords: Ranting, Raving, Muttering, Grumbling}
    {SIGBOVIK_2021_paper_2}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_3}
    {0cm}
\addpaper
    {If It Type-checks, It Works: FoolProof Types As Specifications}
    {Brandon Wu}
    {Keywords: PL, languages, types, specifications, correctness, type-checking, functional programming}
    {SIGBOVIK_2021_paper_40}
    {0cm}
    {}
\addpaper
    {Oracle Types}
    {Akiva Leffert and Jason Reed}
    {Keywords: types, databases, constraints, texting, machine translation, typescript}
    {SIGBOVIK_2021_paper_21}
    {0cm}
    {}
\addpaper
    {Lowestcase and uppestcase letters: Advances in derp learning}
    {Tom Murphy VII}
    {case analysis, derp learning, 3d manifold, chess, exponentiation, fonts}
    {SIGBOVIK_2021_paper_26}
    {0cm}
    {}
\addpaper
    {Dependent Stringly-Typed Programming}
    {gallais}
    {Keywords: dependent stringly typed programming, best practices, agda}
    {SIGBOVIK_2021_paper_34}
    {0cm}
    {}
\addpaper
    {Yet Another Lottery Ticket Hypothesis}
    {Aman Madaan and Gary Yao}
    {Keywords: lottery, random, language models}
    {SIGBOVIK_2021_paper_24}
    {0cm}
    {}

@@

\addtrack
    {}{ApPLied Theory}
\addpaper
    {The Newcomb-Benford Law, Applied to Binary Data: An Empirical and Theoretic Analysis}
    {Gabriel Chuang and Brandon Wu}
    {Keywords: Numerical Methods, Verification, Poor Proof Style, Statistics}
    {SIGBOVIK_2021_paper_41}
    {0cm}
    {}
\addpaper
    {How to get to second base and beyond - a constructive guide for mathematicians}
    {Raluca Jalaboi and Mads Eiler Hansen}
    {Keywords: damn, forgot, again, deadlines}
    {SIGBOVIK_2021_paper_7}
    {0cm}
    {}
\addpaper
    {NetPlop: A moderately-featured presentation editor built in NetLogo}
    {Patrick Steinmann}
    {Keywords: agent-based slideshows, slide-based models, singularity}
    {SIGBOVIK_2021_paper_37}
    {0cm}
    {}

\addtrack{}{(Meta)physics}
\addpaper
    {A Complete Survey of 0-Dimensional Computer Graphics}
    {Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Po Po}
    {Keywords: Computer Graphics, Geometry, Rendering, Animation}
    {SIGBOVIK_2021_paper_30}
    {0cm}
    {}
\addpaper
    {Macro-driven metalanguage for writing Pyramid Scheme programs}
    {Marcin Konowalczyk}
    {Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
    {SIGBOVIK_2021_paper_31}
    {0cm}
    {}
\addpaper
    {On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
    {Zikuan Wang}
    {Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
    {SIGBOVIK_2021_paper_32}
    {0cm}
    {}
\addpaper
    {Inverted Code Theory: Manipulating Program Entropy}
    {usH nalA dna eiX xelA}
    {Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}
    {SIGBOVIK_2021_paper_23}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

>>>>

\newcommand{\link}[2][]{\vspace{-1in} {\scriptsize #1 \url{#2}} \raisebox{-0.5\height}{\includegraphics[height=0.75in]{participation}}}
\newcommand{\badge}[1]{\includegraphics[height=0.75in]{badges/badge_#1}}
\newcommand{\badges}[1]{\vspace{-1in} \raisebox{-0.5\height}{#1}}

\addtrack
    {}{Fun(?) and Games Track}
\addpaper
    {Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
    {Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}
    {Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}
    {SIGBOVIK_2021_paper_5}
    {0cm}
    {\badges{\badge{unusable}}}
\addpaper
    {Demystifying the Mortal Kombat Song}
    {J Devi and Chai-Tea Latte}
    {Keywords: mortal-kombat, truth, meaning-of-life}
    {SIGBOVIK_2021_paper_12}
    {0cm}
    {}
\addpaper
    {Unicode Magic Tricks}
    {Nicolas Hurtubise}
    {Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}
    {SIGBOVIK_2021_paper_13}
    {0cm}
    {}
\addpaper
    {Video games in Fonts Fontemon}
    {Michael Mulet}
    {Keywords: font, video game, font video game, silly idea done seriously}
    {SIGBOVIK_2021_paper_18}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_5}
    {0cm}

\addpaper
    {Soliterrible}
    {Sam Stern}
    {Keywords: solitaire, klondike, cards}
    {SIGBOVIK_2021_paper_27}
    {0cm}
    {\badges{\badge{javascript}}}
\addpaper
    {Opening Moves in 1830: Strategy in Resolving the N-way Prisoner’s Dilemma}
    {Philihp Busby and Daniel Ribeiro E Sousa}
    {Keywords: boardgame, opening, strategy, deterministic, auction}
    {SIGBOVIK_2021_paper_44}
    {0cm}
    {}

@@

\addtrack
    {}{``Type'' Track}
\addpaper
    {Stop Doing Type Theory}
    {}
    {Keywords: Ranting, Raving, Muttering, Grumbling}
    {SIGBOVIK_2021_paper_2}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_3}
    {0cm}
\addpaper
    {If It Type-checks, It Works: FoolProof Types As Specifications}
    {Brandon Wu}
    {Keywords: PL, languages, types, specifications, correctness, type-checking, functional programming}
    {SIGBOVIK_2021_paper_40}
    {0cm}
    {}
\addpaper
    {Oracle Types}
    {Akiva Leffert and Jason Reed}
    {Keywords: types, databases, constraints, texting, machine translation, typescript}
    {SIGBOVIK_2021_paper_21}
    {0cm}
    {\badges{\badge{unavailable}}}
\addpaper
    {Lowestcase and uppestcase letters: Advances in derp learning}
    {Tom Murphy VII}
    {case analysis, derp learning, 3d manifold, chess, exponentiation, fonts}
    {SIGBOVIK_2021_paper_26}
    {0cm}
    {}
\addpaper
    {Dependent Stringly-Typed Programming}
    {gallais}
    {Keywords: dependent stringly typed programming, best practices, agda}
    {SIGBOVIK_2021_paper_34}
    {0cm}
    {\badges{\badge{literate}}}
\addpaper
    {Yet Another Lottery Ticket Hypothesis}
    {Aman Madaan and Gary Yao}
    {Keywords: lottery, random, language models}
    {SIGBOVIK_2021_paper_24}
    {0cm}
    {}

@@

\addtrack
    {}{ApPLied Theory}
\addpaper
    {The Newcomb-Benford Law, Applied to Binary Data: An Empirical and Theoretic Analysis}
    {Gabriel Chuang and Brandon Wu}
    {Keywords: Numerical Methods, Verification, Poor Proof Style, Statistics}
    {SIGBOVIK_2021_paper_41}
    {0cm}
    {}
\addpaper
    {How to get to second base and beyond - a constructive guide for mathematicians}
    {Raluca Jalaboi and Mads Eiler Hansen}
    {Keywords: damn, forgot, again, deadlines}
    {SIGBOVIK_2021_paper_7}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {NetPlop: A moderately-featured presentation editor built in NetLogo}
    {Patrick Steinmann}
    {Keywords: agent-based slideshows, slide-based models, singularity}
    {SIGBOVIK_2021_paper_37}
    {0cm}
    {\badges{\badge{netlogo}}}

\addtrack{}{(Meta)physics}
\addpaper
    {A Complete Survey of 0-Dimensional Computer Graphics}
    {Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Po Po}
    {Keywords: Computer Graphics, Geometry, Rendering, Animation}
    {SIGBOVIK_2021_paper_30}
    {0cm}
    {}
\addpaper
    {Macro-driven metalanguage for writing Pyramid Scheme programs}
    {Marcin Konowalczyk}
    {Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
    {SIGBOVIK_2021_paper_31}
    {0cm}
    {\badges{needs a badge}}
\addpaper
    {On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
    {Zikuan Wang}
    {Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
    {SIGBOVIK_2021_paper_32}
    {0cm}
    {}
\addpaper
    {Inverted Code Theory: Manipulating Program Entropy}
    {usH nalA dna eiX xelA}
    {Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}
    {SIGBOVIK_2021_paper_23}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}
